Viscous Transport in Eroding Porous Media

### 2019-05-13 docs/transport/erosion_transport.tex
add modified figures of transport paper
making small changes

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Boundary Integral Equation Formulation}
\label{s:formulation}
Continuing with our previous work~\cite{qua-moo2018}, we use a completed
double-layer potential formulation for the velocity $\uu$.  The
double-layer potential is
\begin{align}
  \DDD[\eeta](\xx) = \frac{1}{\pi}\int_{\bd\Omega} 
    \frac{\rr \cdot \nn}{\rho^2} \frac{\rr \otimes \rr}{\rho^2}
    \eeta(\yy) \, ds_\yy, \quad \xx \in \Omega,
  \label{eqn:stokesDLP}
\end{align}
where $\rr = \xx - \yy$, $\rho = \|\rr\|$, $\nn$ is the unit outward
normal at $\yy$, and $\eeta$ is an unknown density function.  The Stokes
double-layer potential can be as the sum of the Laplace double-layer
potential and its gradient.  By identifying $\xx,\yy \in \RR^2$ with the
points $x,y \in \CC$, the Laplace double-layer potential for a
real-valued density function $\eta$ can also be written as the real part
of the Cauchy integral
\begin{align}
  \DD[\eta](\xx) = \frac{1}{2\pi} \int_{\bd\Omega}
    \frac{\rr \cdot \nn}{\rho^2} \eta(\yy) ds_\yy = 
  \Re \left( \frac{1}{2\pi i} \int_{\bd\Omega}
    \frac{\eta(y)}{x - y} \, dy \right).
\end{align}
Therefore, the Stokes double-layer potential can be written in terms of
Cauchy integrals and its first derivative.  In addition, we also require
expressions for the derivative of the velocity field which can be
written in terms of a Cauchy integral and its first two derivatives.
Therefore, we introduce the notation
\todo[inline]{BQ: Need to discuss boundary data and how to get it from
density $\eta$}
\begin{align}
  \label{eqn:cauchy}
  v[\eta](x) = \frac{1}{2\pi i} \int_{\bd\Omega}
    \frac{\eta(y)}{x - y} \, dy,  \quad
  v'[\eta](x) = -\frac{1}{2\pi i} \int_{\bd\Omega}
    \frac{\eta(y)}{(x - y)^2} \, dy, \quad
  v''[\eta](x) = \frac{1}{\pi i} \int_{\bd\Omega}
    \frac{\eta(y)}{(x - y)^3} \, dy.
\end{align}
To simplify notation, whenever it will not cause confusion, we exclude
$\tau$ and instead write $v(x)$, $v'(x)$, and $v''(x)$.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Boundary Integral Equation Formulation}
\label{s:formulation}
Continuing with our previous work~\cite{qua-moo2018}, we use a completed
double-layer potential formulation for the velocity $\uu$.  The
double-layer potential is
\begin{align}
  \DDD[\eeta](\xx) = \frac{1}{\pi}\int_{\bd\Omega} 
    \frac{\rr \cdot \nn}{\rho^2} \frac{\rr \otimes \rr}{\rho^2}
    \eeta(\yy) \, ds_\yy, \quad \xx \in \Omega,
  \label{eqn:stokesDLP}
\end{align}
where $\rr = \xx - \yy$, $\rho = \|\rr\|$, $\nn$ is the unit outward
normal at $\yy$, and $\eeta$ is an unknown density function.  The Stokes
double-layer potential can also be expressed as the sum of a Laplace
double-layer potential 
\begin{align}
  \DD[\eta](\xx) = \frac{1}{2\pi} \int_{\bd\Omega}
    \frac{\rr \cdot \nn}{\rho^2} \eta(\yy) ds_\yy
\end{align}
and its gradient.  By identifying $\xx,\yy \in
\RR^2$ with the points $x,y \in \CC$, the Laplace double-layer potential
for a real-valued density function $\eta$ can also be written as the
real part of the Cauchy integral
\begin{align}
  \DD[\eta](\xx) = \Re (v(x)) \quad \text{where} \quad
  v(x) = \frac{1}{2\pi i} \int_{\bd\Omega}
    \frac{\eta(y)}{x - y} \, dy.
\end{align}
Therefore, the Stokes double-layer potential can be written in terms of
Cauchy integrals and its first derivative.  Rather than immediately
applying a quadrature rule to compute $v(x)$, we will first compute the
boundary data of $v(x)$ by applying the Sokhotski-Plemelj jump relation
\begin{align}
  v^{-}(x) = -\frac{1}{2} \eta(x) - \frac{1}{2\pi i} \text{PV}
\end{align}

In addition, we also require
expressions for the derivative of the velocity field which can be
written in terms of a Cauchy integral and its first two derivatives.
Therefore, we introduce the notation
\todo[inline]{BQ: Need to discuss boundary data and how to get it from
density $\eta$}
\begin{align}
  \label{eqn:cauchy}
  v[\eta](x) = \frac{1}{2\pi i} \int_{\bd\Omega}
    \frac{\eta(y)}{x - y} \, dy,  \quad
  v'[\eta](x) = -\frac{1}{2\pi i} \int_{\bd\Omega}
    \frac{\eta(y)}{(x - y)^2} \, dy, \quad
  v''[\eta](x) = \frac{1}{\pi i} \int_{\bd\Omega}
    \frac{\eta(y)}{(x - y)^3} \, dy.
\end{align}
To simplify notation, whenever it will not cause confusion, we exclude
$\tau$ and instead write $v(x)$, $v'(x)$, and $v''(x)$.
